### 2017-01-12 paper/evaluation.tex
Conflict resolved and added explanation on RQ3

@@

\newcommand{\rqA}{\textbf{RQ1.} \RQA}
\newcommand{\rqB}{\textbf{RQ2.} \RQB}
\newcommand{\rqC}{\textbf{RQ3.} \RQC}
\newcommand{\rqD}{\textbf{RQ4.} \RQD}
\newcommand{\rqE}{\textbf{RQ5.} \RQE}
\newcommand{\rqF}{\textbf{RQ6.} \RQF}

\begin{itemize}
    \item \rqA
    \item \rqB
    \item \rqC
    \item \rqD
    \item \rqE
    \item \rqF
\end{itemize}

@@

\subsection{Answering research question RQ1}
\label{sec:rqA}

@@

\subsection{Answering research question RQ2}
\label{sec:rqB}

@@

\subsection{Answering research question RQ3}
\label{sec:rqC}

@@

%% We
%% focused in these two groups because given that costly test suites
%% exist, we investigated if the maintainers are aware of parallelization
%% settings.

To answer RQ3\Mar{use macro} we initially mined build files (\ie,
\pomf{}) that contain parallelization keywords, namely
\CodeIn{forkMode}, \CodeIn{forkCount}, and \CodeIn{parallel}.
According to the Maven surefire documentation\Fix{cite surefire doc},
any configuration to run tests in parallel must contain one of these
keywords. This mining step, however, is not sound as a matching
project may not indicate a project with a valid configuration for
running tests in parallel.  False positive can happen because of
comments, for instance.  To eliminate the cases of false positives and
also to categorize true positive cases, we complemented the initial
mining step with a manual inspection of files.

@@

Figure~\ref{tab:inspection-table} summarizes our results.  Column
``Group'' indicates the group of projects according to their time
cost.\Mar{quickly explain other columns}

%% summarize observations...
From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
where 109\Mar{use macro} of those files match one of the keywords
mentioned above.  From these 109\Mar{use macro} build files, we
eliminated six false-positives: two were names of project modules
(\eg, \emph{camel-cookbook-parallel-processing}), one was part of a
comment, and three were commented configurations. The 106\Fix{fix
  this} build files with valid configurations are distributed across
41\Mar{use macro} projects from our sample.  \emph{From these results
  we found that $\sim$51\% of medium and long-running projects do not
  use parallel features to run test suites.}\Mar{please make it
  consistent with research question}\Mar{explain this is
  over(under)-estimated...}

\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group} & \multirow{2}{*}{\# \pomf{}} & \# \pomf{} matched & \# projects matched\\%
                               &                             &  (false-positives) &       / total\\%
        \midrule%
        Long   & 1613 & 79 (1) & 19/\numLong{}\\%
        Medium & 1238 & 30 (5) & 22/\numMed{}\\%
        \midrule%
        Total  & \pomMedLong{} & 109 (6) & 41/\numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallel configurations in build files from
    projects with time-consuming tests. \Fix{explain columns}}
    \label{tab:inspection-table} 
\end{figure}

@@

\Jbc{Conclusion and relate the results to the
  RQ...........................................}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallelism modes
    identified in \Fix{M} projects\Jbc{Currently medium and partially
    the long group...}}
\end{figure}

\subsection{Answering research question RQ4}
\label{sec:rqD}

>>>>

\newcommand{\numRQA}{RQ1}
\newcommand{\numRQB}{RQ2}
\newcommand{\numRQC}{RQ3}
\newcommand{\numRQD}{RQ4}
\newcommand{\numRQE}{RQ5}
\newcommand{\numRQF}{RQ6}

@@

\begin{itemize}
    \item \textbf{\numRQA.} \RQA
    \item \textbf{\numRQB.} \RQB
    \item \textbf{\numRQC.} \RQC
    \item \textbf{\numRQD.} \RQD
    \item \textbf{\numRQE.} \RQE
    \item \textbf{\numRQF.} \RQF
\end{itemize}

@@

\subsection{Answering research question \numRQA{}}
\label{sec:rqA}

@@

\subsection{Answering research question \numRQB{}}
\label{sec:rqB}

@@

\subsection{Answering research question \numRQC{}}
\label{sec:rqC}

@@

To answer \numRQC{} we initially mined build files (\ie, \pomf{}) that
contain parallelization keywords, namely \CodeIn{forkMode},
\CodeIn{forkCount}, and \CodeIn{parallel}.  According to the Maven
surefire documentation\Fix{cite surefire doc}, any configuration to
run tests in parallel must contain one of these keywords. This mining
step, however, is not sound as a matching project may not indicate a
project with a valid configuration for running tests in parallel.
False positive can happen because of comments, for instance.  To
eliminate the cases of false positives and also to categorize true
positive cases, we complemented the initial mining step with a manual
inspection of files.

@@

Figure~\ref{tab:inspection-table} summarizes our results. The first
column indicates the group of projects according to their time cost.
The second column indicates the number of build files per group.  The
third column is a subset from the previous column and represents the
number of build files found in the mining step (including
false-positives highlighted in parentheses). The last column indicates
the ratio of projects with parallelization settings.

From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
where \numPomMatched{} of those files match one of the keywords
mentioned above.  From these \numPomMatched{} build files, we
eliminated six false-positives: two were names of project modules
(\eg, \emph{camel-cookbook-parallel-processing}), one was part of a
comment, and three were commented configurations. The
\numPomMatchedValid{} build files with valid configurations are
distributed across \numProjectsPar{} projects from our sample.
\emph{From these results we found that $\sim$51\% of medium and
long-running projects do not use parallel features to run test
suites.}\Mar{please make it consistent with research
question}\Mar{explain this is over(under)-estimated...}

\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group}
            & \multirow{2}{*}{\# \pomf{}}
            & \# \pomf{} matched
            & \# projects matched\\%
        % 2nd row - empty cell
            & % empty cell
            & (false-positives)
            & / total\\%
        \midrule%
        Long   & 1613 & 79 (1) & 19 / \numLong{}\\%
        Medium & 1238 & 30 (5) & 22 / \numMed{}\\%
        \midrule%
        Total & \pomMedLong{} & \numPomMatched{} (6) & \numProjectsPar{} / \numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallelization settings in build files: the
    first column indicates the group of projects according to their
    time cost; the second column indicates the number of build files;
    the third column is the subset of files with parallelization
    keywords; the last column indicates the ratio of projects with
    parallelism support.}
    \label{tab:inspection-table} 
\end{figure}

@@

From the \numProjectsPar{} projects identified above, we investigated
further the \numPomMatchedValid{} build files with parallel settings.
We analyzed the support and distribution of parallel modes from this
subset of projects. To calculate the distribution of parallel modes,
we considered only the presence of the mode in at least one of the
project settings.  Recall that a build file may contain more than one
parallel setting and a project may contain several sub-modules with
build files.  In case the value of a parallel option is resolved
dynamically (\eg, via command-line argument or system variable) we
compute all modes related to the option. For instance, depending on
the value, the \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes} summarizes our findings.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallel modes
    identified in a subset of \numProjectsPar{} projects. A single
    project may have support to more than one parallel mode.}
\end{figure}

\subsection{Answering research question \numRQD{}}
\label{sec:rqD}
